07_summary_stats

### 2023-10-20 07_summary_stats.Rmd
Update 07_summary_stats.Rmd
removed BWC and BW37V

# One detection value for BWC
BWC <- allDrifts %>%
  dplyr::filter(species == "BWC")
print(paste("BWC Max TOL125 sound level: ", max(BWC$TOL_125, na.rm = TRUE)))
print(paste("BWC Min TOL125 sound level: ", min(BWC$TOL_125, na.rm = TRUE)))
print(paste("BWC Max TOL20000 sound level: ", max(BWC$TOL_2000, na.rm = TRUE)))
print(paste("BWC Min TOL20000 sound level: ", min(BWC$TOL_2000, na.rm = TRUE)))

@@

BW37V <- allDrifts %>%
  dplyr::filter(species == "BW37V")
print(paste("BW37V Max TOL125 sound level: ", max(BW37V$TOL_125, na.rm = TRUE)))
print(paste("BW37V Min TOL125 sound level: ", min(BW37V$TOL_125, na.rm = TRUE)))
print(paste("BW37V Max TOL20000 sound level: ", max(BW37V$TOL_2000, na.rm = TRUE)))
print(paste("BW37V Min TOL20000 sound level: ", min(BW37V$TOL_2000, na.rm = TRUE)))

@@

ZC <- allDrifts %>%
  dplyr::filter(species == "ZC")
print(paste("ZC Max TOL125 sound level: ", max(ZC$TOL_125, na.rm = TRUE)))
print(paste("ZC Min TOL125 sound level: ", min(ZC$TOL_125, na.rm = TRUE)))
print(paste("ZC Max TOL20000 sound level: ", max(ZC$TOL_2000, na.rm = TRUE)))
print(paste("ZC Min TOL20000 sound level: ", min(ZC$TOL_2000, na.rm = TRUE)))
```

@@

print(paste("Number of PM detections: ", nrow(PM)))
print(paste("Number of ZC detections: ", nrow(ZC)))
print(paste("Number of BW43 detections: ", nrow(BW43)))
print(paste("Number of BWC detections: ", nrow(BWC)))
print(paste("Number of BB detections: ", nrow(BB)))
print(paste("Number of BW37V detections: ", nrow(BW37V)))

>>>>

@@

@@

ZC <- allDrifts %>%
  dplyr::filter(species == "ZC")
print(paste("ZC Max TOL125 sound level: ", max(ZC$TOL_125, na.rm = TRUE)))
print(paste("ZC Min TOL125 sound level: ", min(ZC$TOL_125, na.rm = TRUE)))
print(paste("ZC Max TOL20000 sound level: ", max(ZC$TOL_2000, na.rm = TRUE)))
print(paste("ZC Min TOL20000 sound level: ", min(ZC$TOL_2000, na.rm = TRUE)))

@@

print(paste("Number of PM detections: ", nrow(PM)))
print(paste("Number of ZC detections: ", nrow(ZC)))
print(paste("Number of BW43 detections: ", nrow(BW43)))
print(paste("Number of BB detections: ", nrow(BB)))
